### 2018-08-01 Sections/network_topologies.tex
Percolations, dblfloatfix

%
% Random
%

\subsection{Random} \index{Random topologies}

A variation on the complete graph, $K_{|V|}$, is to instead have a randomised implementation of it, whereby each of the possible edges in $K_{|V|}$ occurs with probability \mbox{$0\leq p_\mathrm{edge}\leq 1$}. We would thereby be able to tune between the complete graph and the completely disconnected graph, representing a randomly connected network with arbitrary average connectivity. Specifically, the average number of links emanating from any node is \mbox{$e_\mathrm{av} = (|V|-1)p_\mathrm{edge}$}. Note that random graphs might be disjoint, making them inappropriate for many networking applications. For asymptotically large random graphs, \textit{percolation theory} \cite{???} provides thresholds for $p_\mathrm{edge}$ such that they remain connected \cite{???}. Fig.~\ref{fig:random_graph} illustrates several graphs with different edge connectivity probabilities.

\begin{figure*}[!htb]
\includegraphics[width=0.325\textwidth]{random_0}
\includegraphics[width=0.325\textwidth]{random_05}
\includegraphics[width=0.325\textwidth]{random_1}
\caption{The 15-vertex randomly-connected graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\mathrm{edge}=0,0.5,1$} (top to bottom).} \label{fig:random_graph}
\end{figure*}

Random graphs capture the ad hoc nature of networks that exhibit no planned structure, but are rather cobbled together in a completely improvised manner.

>>>>

%
% Percolation
%

\subsection{Percolation}\index{Percolation graph}

A variation on any graph, $G$, is to instead have a randomised implementation of it, whereby each of the possible edges \mbox{$e\in E$} or vertices \mbox{$v\in V$} occurs with some probability \mbox{$0\leq p_\mathrm{perc}\leq 1$}. These are referred to as \textit{edge percolation} and \textit{site percolation} graphs respectively.

Adjusting $p_\mathrm{perc}$ allows us to tune between the desired graph (when $p_\mathrm{perc}=1$) and the completely disconnected graph (when $p_\mathrm{perc}=0$). This model is very useful in real-world applications, allowing unreliable channels/nodes to be incorporated into our network model. The analysis of such percolation networks is invaluable for understanding the robustness of such networks to channel and node failures.

%The average number of links emanating from any node is \mbox{$e_\mathrm{av} = (|V|-1)p_\mathrm{edge}$}.

Note that percolation graphs might be disjoint with sufficient defects, in which case the respective network becomes unreliable. Specifically, with sufficiently low $p_\mathrm{perc}$, `islands' may form in the network topology -- small segregated networks, which are unable to interface with the remainder of the network.

For asymptotically large percolation graphs, \textit{percolation theory}\index{Percolation theory} \cite{???} provides thresholds for $p_\mathrm{perc}$ such that routes across the network exist \cite{???}.

Fig.~\ref{fig:perc_graph} illustrates several graphs with different percolation probabilities, and how the larger network segregates into smaller islands as failure rates increase.

\begin{figure*}[!htb]
\includegraphics[width=0.325\textwidth]{random_0}
\includegraphics[width=0.325\textwidth]{random_05}
\includegraphics[width=0.325\textwidth]{random_1}\\
\includegraphics[width=0.325\textwidth]{percolation_1}
\includegraphics[width=0.325\textwidth]{percolation_2}
\includegraphics[width=0.325\textwidth]{percolation_3}
\caption{(top) The 15-vertex randomly-connected percolation graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\mathrm{edge}=0,0.5,1$} (top to bottom). (bottom) A square lattice graph subject to different percolation rates (node defects). As the failure rate increases, the larger network segregates into smaller disjoint islands (denoted by colour).} \label{fig:perc_graph}
\end{figure*}

### 2018-08-01 Sections/protocols_for_the_quantum_internet.tex
Percolations, dblfloatfix

Linear optics networks implement unitary linear maps on the photonic creation operators, of the form,
\begin{align} \label{eq:LO_unitary_map}
\hat{U}\hat{a}_i^\dag \hat{U}^\dag \to \sum_{j=1}^m U_{i,j} \hat{a}^\dag_j,
\end{align}
where $\hat{a}^\dag_i$ is the photonic creation operator on the $i$th of the $m$ modes, and $U$ may be any $\mathrm{SU}(m)$ matrix. It was shown by \cite{bib:Reck94} that arbitrary transformations of this form may be decomposed into $O(m^2)$ linear optical elements (beamsplitters and phase-shifters), enabling efficient construction of arbitrary linear transformations.\index{Linear optics decompositions} Furthermore, the algorithm for determining the decomposition of such transformations has polynomial classical runtime (i.e residing in \textbf{P}\index{P}). Note that the original Reck \textit{et al.} decomposition is not unique, and various other topologies of optical elements also enable universality \cite{???}.

@@

These linear optics evolutions are most commonly implemented using either:
\begin{itemize}
\item Bulk optics: where discrete optical elements are arranged on an optical table.\index{Bulk optics}
\item Time-bin architectures: where time-bin encoded qubits (Sec.~\ref{sec:time_bin}) evolve through delay lines and interfere at a single central optical component.\index{Time-bin encoding}\index{Fibre-loops}
\item Integrated waveguides: where all passive components are etched into a chip.\index{Waveguides}
\end{itemize}
These three main contenders are illustrated in Fig.~\ref{fig:LO_archs}, and described in more detail in Sec.~\ref{sec:LO_evolution}.

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{LO_archs}
\caption{The three primary approaches for implementing linear optics transformations. (a) Bulk optics\index{Bulk optics}, where each optical mode is spatially encoded, and the linear transformation is decomposed into a discrete array of beamsplitters and phase-shifters, an appropriate choice of which enables arbitrary linear optics transformations to be implemented. (b) Time-bin encoding\index{Time-bin encoding}\index{Fibre-loops}, where each optical mode is designated a distinct time-bin. Fibre-loops meeting at dynamically reconfigurable beamsplitters enable arbitrary linear transformations to be implemented. (c) Integrated wave-guide chips\index{Waveguides}, where evanescent coupling between neighbouring wave-guides within a chip facilitates interference between modes (graphic courtesy of Alberto Peruzzo \cite{bib:PeruzzoQW}). (d) Integrated wave-guide chip with electrically controllable phase-shifters, implementing a programmable, universal \mbox{$6\times 6$} linear optics network (graphic courtesy of Jeremy O'Brien \cite{bib:UniversalLOOBrien}).} \label{fig:LO_archs}
\end{figure}

>>>>

Linear optics networks \cite{bib:TanRohdeRev} implement unitary linear maps on the photonic creation operators, of the form,
\begin{align} \label{eq:LO_unitary_map}
\hat{U}\hat{a}_i^\dag \hat{U}^\dag \to \sum_{j=1}^m U_{i,j} \hat{a}^\dag_j,
\end{align}
where $\hat{a}^\dag_i$ is the photonic creation operator on the $i$th of the $m$ modes, and $U$ may be any $\mathrm{SU}(m)$ matrix. It was shown by \cite{bib:Reck94} that arbitrary transformations of this form may be decomposed into $O(m^2)$ linear optical elements (beamsplitters and phase-shifters), enabling efficient construction of arbitrary linear transformations.\index{Linear optics decompositions} Furthermore, the algorithm for determining the decomposition of such transformations has polynomial classical runtime (i.e residing in \textbf{P}\index{P}). Note that the original Reck \textit{et al.} decomposition is not unique, and various other topologies of optical elements also enable universality \cite{???}.

@@

These linear optics evolutions are most commonly implemented using either:
\begin{itemize}
\item Bulk optics: discrete optical elements are arranged on an optical table.\index{Bulk optics}
\item Time-bin architectures: time-bin encoded qubits (Sec.~\ref{sec:time_bin}) evolve through delay lines and interfere at a single central optical component.\index{Time-bin encoding}\index{Fibre-loops}
\item Integrated waveguides: all passive components are etched into a chip.\index{Waveguides}
\end{itemize}
These three main contenders are illustrated in Fig.~\ref{fig:LO_archs}.

\begin{figure*}[!htb]
\includegraphics[width=\textwidth]{LO_archs}
\caption{The three primary approaches for implementing linear optics transformations. (a) Bulk optics\index{Bulk optics}, where each optical mode is spatially encoded, and the linear transformation is decomposed into a discrete array of beamsplitters and phase-shifters, an appropriate choice of which enables arbitrary linear optics transformations to be implemented. (b) Time-bin encoding\index{Time-bin encoding}\index{Fibre-loops}, where each optical mode is designated a distinct time-bin. Fibre-loops meeting at dynamically reconfigurable beamsplitters enable arbitrary linear transformations to be implemented. (c) Integrated wave-guide chips\index{Waveguides}, where evanescent coupling between neighbouring wave-guides within a chip facilitates interference between modes (graphic courtesy of Alberto Peruzzo \cite{bib:PeruzzoQW}). (d) Integrated wave-guide chip with electrically controllable phase-shifters, implementing a programmable, universal \mbox{$6\times 6$} linear optics network (graphic courtesy of Jeremy O'Brien \cite{bib:UniversalLOOBrien}\comment{Get permission}).} \label{fig:LO_archs}
\end{figure*}
